Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records

### 2025-01-18 MANUSCRIPT.qmd
Update MANUSCRIPT.qmd

---
title: Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records
subtitle: Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands |  | Estimating Base-Flow Index in Gauged and Ungauged Dryland Basins
author:
  - name: Caelum Mroczek
    orcid: 0009-0005-6695-0134
    corresponding: true
    email: csm428@nau.edu
    roles:
      - Conceptualization
      - Investigation
      - Methodology
      - Formal analysis
      - Visualization
      - Software
      - Data curation
      - Writing - Original Draft
    affiliations:
      - 'School of Earth and Sustainability, Northern Arizona University, Flagstaff, AZ, USA'

  - name: Abraham Springer
    orcid: 0000-0003-4826-9124
    corresponding: false
    roles: []
    affiliations:
      - 'School of Earth and Sustainability, Northern Arizona University, Flagstaff, AZ, USA'

  - name: Neha Gupta
    orcid: 0000-0002-2247-3509
    corresponding: false
    roles: []
    affiliations:
      - 'Department of Hydrology and Atmospheric Sciences, University of Arizona, Tucson, AZ, USA'

  - name: Benjamin Lucas
    orcid: 0000-0002-2021-3076
    corresponding: false
    roles: []
    affiliations:
      - 'Department of Mathematics and Statistics, Northern Arizona University, Flagstaff, AZ, USA'

>>>>

---
title: Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records
subtitle: Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands |  | Estimating Base-Flow Index in Gauged and Ungauged Dryland Basins
author:
  - name: Caelum Mroczek
    orcid: 0009-0005-6695-0134
    corresponding: true
    email: csm428@nau.edu
    roles:
      - Conceptualization
      - Investigation
      - Methodology
      - Formal analysis
      - Visualization
      - Software
      - Data curation
      - Writing - Original Draft
      - Writing – Review & Editing 
    affiliations:
      - 'School of Earth and Sustainability, Northern Arizona University, Flagstaff, AZ, USA'

  - name: Abraham Springer
    orcid: 0000-0003-4826-9124
    corresponding: false
    roles:
      - Conceptualization
      - Funding acquisition
      - Project administration
      - Resources
      - Supervision
      - Writing – Review & Editing 
    affiliations:
      - 'School of Earth and Sustainability, Northern Arizona University, Flagstaff, AZ, USA'

  - name: Neha Gupta
    orcid: 0000-0002-2247-3509
    corresponding: false
    roles: 
      - Conceptualization
      - Funding acquisition
      - Project administration
      - Resources
      - Supervision
      - Writing – Review & Editing 
    affiliations:
      - 'Department of Hydrology and Atmospheric Sciences, University of Arizona, Tucson, AZ, USA'

  - name: Benjamin Lucas
    orcid: 0000-0002-2021-3076
    corresponding: false
    roles: 
      - Conceptualization
      - Resources
      - Supervision
      - Software
      - Writing – Review & Editing 
    affiliations:
      - 'Department of Mathematics and Statistics, Northern Arizona University, Flagstaff, AZ, USA'
